String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-04 2023-1-19/figures/cactus_plot_regexlib.tex
experiment done

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourOstrichCEA}{HTML}{25333D}
\definecolor{colourCVC5}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=regexlib,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.326)(8.5,14.001375)(24.5,39.800875)(40.5,67.09)(56.5,95.3169375)(72.5,124.4550625)(88.5,154.267375)(104.5,184.69425)(120.5,215.657)(136.5,247.035125)(152.5,278.7906875)(168.5,311.0410625)(184.5,343.8286875)(200.5,377.011375)(216.5,410.68275)(232.5,444.867875)(248.5,479.5120625)(264.5,514.5951875)(280.5,550.083625)(296.5,585.994125)(312.5,622.261875)(328.5,658.8564375)(344.5,695.7899375)(360.5,733.01425)(376.5,770.5569375)(392.5,808.4133125)(408.5,846.6525625)(424.5,885.256)(440.5,924.2085625)(456.5,963.6601875)(472.5,1003.5794375)(488.5,1043.8909375)(504.5,1084.5918125)(520.5,1125.6925625)(536.5,1167.1688125)(552.5,1209.008)(568.5,1251.1431875)(584.5,1293.6194375)(600.5,1336.5265625)(616.5,1379.7884375)(632.5,1423.3959375)(648.5,1467.445375)(664.5,1512.1114375)(680.5,1557.229625)(696.5,1602.6933125)(712.5,1648.5414375)(728.5,1694.74525)(744.5,1741.259875)(760.5,1788.104625)(776.5,1835.441375)(792.5,1883.3281875)(808.5,1931.6915625)(824.5,1980.545125)(840.5,2029.794125)(856.5,2079.47)(872.5,2129.7085625)(888.5,2180.5180625)(904.5,2232.03075)(920.5,2284.4146875)(936.5,2337.7085)(952.5,2391.664625)(968.5,2446.13225)(984.5,2501.088125)(1000.5,2556.4926875)(1016.5,2612.4775)(1032.5,2669.06175)(1048.5,2726.1491875)(1064.5,2783.9013125)(1080.5,2842.3911875)(1096.5,2901.65625)(1112.5,2961.713625)(1128.5,3022.462)(1144.5,3084.2588125)(1160.5,3146.9798125)(1176.5,3210.752125)(1192.5,3275.4954375)(1208.5,3341.271875)(1224.5,3408.4449375)(1240.5,3476.9365625)(1256.5,3546.931625)(1272.5,3618.58925)(1288.5,3691.8859375)(1304.5,3767.448375)(1320.5,3845.036625)(1336.5,3924.75)(1352.5,4006.6775)(1368.5,4090.948625)(1384.5,4177.0058125)(1400.5,4266.37675)(1416.5,4358.8839375)(1432.5,4454.4639375)(1448.5,4553.3179375)(1464.5,4656.1215625)(1480.5,4765.12675)(1496.5,4880.6024375)(1512.5,5003.2408125)(1528.5,5136.673125)(1544.5,5283.0321875)(1560.5,5444.2958125)(1576.5,5642.1679375)(1592.5,5967.94825)(1602,6241.055)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(8.5,0.0501875)(24.5,0.1841875)(40.5,0.385375)(56.5,0.63275)(72.5,0.9063125)(88.5,1.2073125)(104.5,1.53075)(120.5,1.878625)(136.5,2.248)(152.5,2.6435)(168.5,3.0511875)(184.5,3.4775625)(200.5,3.919)(216.5,4.3756875)(232.5,4.8543125)(248.5,5.36475)(264.5,5.91125)(280.5,6.499375)(296.5,7.1506875)(312.5,7.8543125)(328.5,8.594375)(344.5,9.3725)(360.5,10.1935625)(376.5,11.092875)(392.5,12.035125)(408.5,13.0169375)(424.5,14.058375)(440.5,15.1575625)(456.5,16.3101875)(472.5,17.5235)(488.5,18.79075)(504.5,20.1346875)(520.5,21.5568125)(536.5,23.0485)(552.5,24.6221875)(568.5,26.2756875)(584.5,28.0125625)(600.5,29.863375)(616.5,31.8353125)(632.5,33.9231875)(648.5,36.124625)(664.5,38.4406875)(680.5,40.8851875)(696.5,43.4551875)(712.5,46.18625)(728.5,49.20325)(744.5,52.4388125)(760.5,55.897625)(776.5,59.6255)(792.5,63.556125)(808.5,67.7344375)(824.5,72.17275)(840.5,76.87375)(856.5,81.881625)(872.5,87.2705625)(888.5,92.9146875)(904.5,98.791)(920.5,104.930125)(936.5,111.3364375)(952.5,118.0683125)(968.5,125.098375)(984.5,132.4871875)(1000.5,140.3285625)(1016.5,148.5753125)(1032.5,157.201)(1048.5,166.2395)(1064.5,175.6414375)(1080.5,185.51025)(1096.5,195.957375)(1112.5,207.0698125)(1128.5,218.7384375)(1144.5,231.084125)(1160.5,244.2318125)(1176.5,257.92525)(1192.5,272.16775)(1208.5,287.037)(1224.5,302.7649375)(1240.5,319.7085625)(1256.5,337.873375)(1272.5,357.1653125)(1288.5,377.8138125)(1304.5,399.751125)(1320.5,424.0613125)(1336.5,450.661375)(1352.5,478.92)(1368.5,509.38125)(1384.5,543.107)(1400.5,581.489375)(1416.5,625.1093125)(1432.5,675.3388125)(1448.5,738.061)(1464.5,823.3106875)(1480.5,947.367625)(1496.5,1193.47425)(1512.5,1639.0449375)(1525,2121.9135555555554)(1531,2376.002)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,1.017)(8,10.258933333333333)(23,29.255599999999998)(38,50.394800000000004)(53,72.92853333333333)(68,96.32026666666667)(83,120.54106666666667)(98,145.43706666666668)(113,170.85453333333334)(128,196.90246666666667)(143,223.42426666666665)(158,250.6794)(173,278.59159999999997)(188,307.04659999999996)(203,336.0550666666667)(218,365.4665333333333)(233,395.2475333333333)(248,425.3532)(263,455.8623333333333)(278,486.82626666666664)(293,518.2761333333334)(308,550.2016666666666)(323,582.5965333333334)(338,615.5299333333334)(353,648.8835333333333)(368,682.6476)(383,716.8438000000001)(398,751.3936)(413,786.4327333333333)(428,821.8758)(443,857.6266666666667)(458,893.7378666666667)(473,930.2567333333333)(488,967.1976)(503,1004.5210666666667)(518,1042.2291333333333)(533,1080.4326)(548,1119.0616666666667)(563,1158.132)(578,1197.6022666666665)(593,1237.5477333333333)(608,1278.0738666666666)(623,1319.0354)(638,1360.3044666666665)(653,1401.9102)(668,1443.9781333333333)(683,1486.5155333333335)(698,1529.4671333333333)(713,1573.0057333333334)(728,1617.0829333333334)(743,1661.8119333333334)(758,1707.0376)(773,1752.8307333333335)(788,1799.0442666666665)(803,1845.8358666666668)(818,1893.2626)(833,1941.298)(848,1990.1431333333333)(863,2039.6957333333335)(878,2089.9846666666667)(893,2141.0992666666666)(908,2193.0147333333334)(923,2245.761466666667)(938,2299.109466666667)(953,2353.2702666666664)(968,2408.4814666666666)(983,2464.6888)(998,2521.7824)(1013,2579.9236666666666)(1028,2639.587466666667)(1043,2701.1523333333334)(1058,2764.0695333333333)(1073,2827.9558666666667)(1088,2893.3823333333335)(1103,2960.3417999999997)(1118,3029.4202666666665)(1133,3100.2347999999997)(1148,3173.076866666667)(1163,3248.1202000000003)(1178,3326.137866666667)(1193,3407.703)(1208,3491.8776666666663)(1223,3578.656933333333)(1238,3668.5506)(1253,3762.1326666666664)(1268,3859.274933333333)(1283,3961.9732666666664)(1298,4070.4924666666666)(1313,4186.787066666667)(1328,4310.513400000001)(1343,4445.3554)(1358,4594.592466666667)(1373,4759.808933333334)(1388,4944.383400000001)(1403,5149.614333333333)(1418,5387.352599999999)(1433,5664.111533333333)(1448,5990.5318)(1463,6394.039400000001)(1478,6895.506266666666)(1493,7542.774266666666)(1502,7966.798)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.014)(8,0.1492666666666667)(23,0.43839999999999996)(38,0.7554)(53,1.0912666666666666)(68,1.446)(83,1.8062)(98,2.176)(113,2.551)(128,2.929)(143,3.318)(158,3.7084)(173,4.109)(188,4.517)(203,4.936)(218,5.362066666666666)(233,5.7984)(248,6.246666666666667)(263,6.708)(278,7.1781999999999995)(293,7.658066666666667)(308,8.147)(323,8.6444)(338,9.153)(353,9.669066666666668)(368,10.1942)(383,10.729)(398,11.269666666666666)(413,11.821)(428,12.376666666666667)(443,12.943)(458,13.514)(473,14.0964)(488,14.692)(503,15.2944)(518,15.9082)(533,16.533)(548,17.166666666666668)(563,17.8124)(578,18.47)(593,19.130666666666666)(608,19.802)(623,20.48)(638,21.169)(653,21.8642)(668,22.576)(683,23.3012)(698,24.039)(713,24.7904)(728,25.5542)(743,26.329066666666666)(758,27.1184)(773,27.927)(788,28.7524)(803,29.591866666666665)(818,30.448)(833,31.318)(848,32.201)(863,33.09986666666667)(878,34.01673333333333)(893,34.955666666666666)(908,35.91266666666667)(923,36.887)(938,37.8816)(953,38.8984)(968,39.93533333333333)(983,41.0048)(998,42.1114)(1013,43.2494)(1028,44.419066666666666)(1043,45.62166666666666)(1058,46.864466666666665)(1073,48.1382)(1088,49.4416)(1103,50.77926666666667)(1118,52.1594)(1133,53.60013333333333)(1148,55.10326666666667)(1163,56.676)(1178,58.32373333333333)(1193,60.0458)(1208,61.842400000000005)(1223,63.705933333333334)(1238,65.68766666666667)(1253,67.79246666666666)(1268,70.0094)(1283,72.42713333333333)(1298,75.1118)(1313,78.03226666666666)(1328,81.21066666666667)(1343,84.72706666666667)(1358,88.56126666666667)(1373,93.02126666666666)(1388,98.26266666666668)(1403,104.86593333333333)(1418,113.51339999999999)(1433,124.53553333333333)(1448,142.9748)(1463,195.25526666666667)(1473.5,343.9191666666667)(1478,471.791)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.014)(8.5,0.1705625)(24.5,0.5270625)(40.5,0.9435)(56.5,1.411375)(72.5,1.9261875)(88.5,2.471375)(104.5,3.0486875)(120.5,3.6491875)(136.5,4.26925)(152.5,4.9183125)(168.5,5.59575)(184.5,6.2953125)(200.5,7.0183125)(216.5,7.7696875)(232.5,8.552625)(248.5,9.361625)(264.5,10.20875)(280.5,11.08875)(296.5,11.9946875)(312.5,12.9349375)(328.5,13.899875)(344.5,14.886625)(360.5,15.894625)(376.5,16.93)(392.5,18.009)(408.5,19.1270625)(424.5,20.2855625)(440.5,21.4935)(456.5,22.751125)(472.5,24.069375)(488.5,25.446875)(504.5,26.8915)(520.5,28.4119375)(536.5,30.015375)(552.5,31.7089375)(568.5,33.4641875)(584.5,35.2725)(600.5,37.1615)(616.5,39.151125)(632.5,41.2473125)(648.5,43.431625)(664.5,45.6884375)(680.5,48.03575)(696.5,50.4545)(712.5,52.9450625)(728.5,55.5413125)(744.5,58.2293125)(760.5,60.9836875)(776.5,63.813375)(792.5,66.7405)(808.5,69.76075)(824.5,72.8876875)(840.5,76.128)(856.5,79.4839375)(872.5,82.9761875)(888.5,86.62225)(904.5,90.3834375)(920.5,94.26825)(936.5,98.3461875)(952.5,102.5914375)(968.5,107.029625)(984.5,111.6445625)(1000.5,116.4698125)(1016.5,121.504625)(1032.5,126.7716875)(1048.5,132.2453125)(1064.5,137.9896875)(1080.5,144.0614375)(1096.5,150.38)(1112.5,156.9101875)(1128.5,163.803625)(1144.5,171.048375)(1160.5,178.675875)(1176.5,186.5573125)(1192.5,194.7738125)(1208.5,203.287375)(1224.5,212.0685)(1240.5,221.080125)(1256.5,230.4013125)(1272.5,240.2630625)(1288.5,250.769125)(1304.5,261.9256875)(1320.5,273.955125)(1336.5,286.6981875)(1352.5,300.027625)(1368.5,314.1886875)(1384.5,329.4320625)(1400.5,345.72025)(1416.5,363.0874375)(1432.5,381.555625)(1448.5,401.5385)(1464.5,423.8074375)(1480.5,448.4118125)(1496.5,476.286125)(1512.5,510.4356875)(1528.5,553.1431875)(1544.5,607.709625)(1560.5,678.581375)(1576.5,800.2424375)(1587,950.0282)(1591,1061.191)};
\addlegendentry{Z3seq}

\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.005)(8.5,0.0531875)(24.5,0.1518125)(40.5,0.2625)(56.5,0.3745)(72.5,0.4865)(88.5,0.5985)(104.5,0.7105)(120.5,0.8253125)(136.5,0.952)(152.5,1.08)(168.5,1.208)(184.5,1.336)(200.5,1.464375)(216.5,1.6035)(232.5,1.7475)(248.5,1.8915)(264.5,2.0355)(280.5,2.1795)(296.5,2.3235)(312.5,2.4675)(328.5,2.6116875)(344.5,2.766)(360.5,2.926)(376.5,3.086)(392.5,3.246)(408.5,3.406)(424.5,3.566)(440.5,3.726)(456.5,3.8873125)(472.5,4.0605)(488.5,4.2365)(504.5,4.4125)(520.5,4.5885)(536.5,4.7645)(552.5,4.9439375)(568.5,5.135)(584.5,5.327)(600.5,5.519)(616.5,5.7175625)(632.5,5.9255)(648.5,6.134125)(664.5,6.354)(680.5,6.5789375)(696.5,6.8155)(712.5,7.056125)(728.5,7.308)(744.5,7.568125)(760.5,7.840125)(776.5,8.124)(792.5,8.4185625)(808.5,8.7234375)(824.5,9.04)(840.5,9.3665625)(856.5,9.7038125)(872.5,10.053)(888.5,10.4084375)(904.5,10.7755)(920.5,11.147625)(936.5,11.5323125)(952.5,11.9296875)(968.5,12.340625)(984.5,12.7685)(1000.5,13.2081875)(1016.5,13.66875)(1032.5,14.14875)(1048.5,14.64475)(1064.5,15.15725)(1080.5,15.691375)(1096.5,16.2514375)(1112.5,16.8374375)(1128.5,17.4513125)(1144.5,18.10075)(1160.5,18.782875)(1176.5,19.5125)(1192.5,20.281875)(1208.5,21.093125)(1224.5,21.9540625)(1240.5,22.867)(1256.5,23.8339375)(1272.5,24.876125)(1288.5,26.007125)(1304.5,27.2279375)(1320.5,28.564875)(1336.5,29.9903125)(1352.5,31.529875)(1368.5,33.237)(1384.5,35.1899375)(1400.5,37.4680625)(1416.5,40.07125)(1432.5,43.1341875)(1448.5,46.8099375)(1464.5,51.341)(1480.5,57.03675)(1496.5,64.4295)(1512.5,73.6899375)(1528.5,86.0960625)(1544.5,108.3425)(1560.5,174.1435625)(1569.5,260.0555)(1572,300.23)};
\addlegendentry{Z3str3RE}

>>>>

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourCVC5}{HTML}{25333D}
\definecolor{colourOstrichCEA}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=regexlib,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt, solid] coordinates {(1,1.326)(8.5,14.001375)(24.5,39.800875)(40.5,67.09)(56.5,95.3169375)(72.5,124.4550625)(88.5,154.267375)(104.5,184.69425)(120.5,215.657)(136.5,247.035125)(152.5,278.7906875)(168.5,311.0410625)(184.5,343.8286875)(200.5,377.011375)(216.5,410.68275)(232.5,444.867875)(248.5,479.5120625)(264.5,514.5951875)(280.5,550.083625)(296.5,585.994125)(312.5,622.261875)(328.5,658.8564375)(344.5,695.7899375)(360.5,733.01425)(376.5,770.5569375)(392.5,808.4133125)(408.5,846.6525625)(424.5,885.256)(440.5,924.2085625)(456.5,963.6601875)(472.5,1003.5794375)(488.5,1043.8909375)(504.5,1084.5918125)(520.5,1125.6925625)(536.5,1167.1688125)(552.5,1209.008)(568.5,1251.1431875)(584.5,1293.6194375)(600.5,1336.5265625)(616.5,1379.7884375)(632.5,1423.3959375)(648.5,1467.445375)(664.5,1512.1114375)(680.5,1557.229625)(696.5,1602.6933125)(712.5,1648.5414375)(728.5,1694.74525)(744.5,1741.259875)(760.5,1788.104625)(776.5,1835.441375)(792.5,1883.3281875)(808.5,1931.6915625)(824.5,1980.545125)(840.5,2029.794125)(856.5,2079.47)(872.5,2129.7085625)(888.5,2180.5180625)(904.5,2232.03075)(920.5,2284.4146875)(936.5,2337.7085)(952.5,2391.664625)(968.5,2446.13225)(984.5,2501.088125)(1000.5,2556.4926875)(1016.5,2612.4775)(1032.5,2669.06175)(1048.5,2726.1491875)(1064.5,2783.9013125)(1080.5,2842.3911875)(1096.5,2901.65625)(1112.5,2961.713625)(1128.5,3022.462)(1144.5,3084.2588125)(1160.5,3146.9798125)(1176.5,3210.752125)(1192.5,3275.4954375)(1208.5,3341.271875)(1224.5,3408.4449375)(1240.5,3476.9365625)(1256.5,3546.931625)(1272.5,3618.58925)(1288.5,3691.8859375)(1304.5,3767.448375)(1320.5,3845.036625)(1336.5,3924.75)(1352.5,4006.6775)(1368.5,4090.948625)(1384.5,4177.0058125)(1400.5,4266.37675)(1416.5,4358.8839375)(1432.5,4454.4639375)(1448.5,4553.3179375)(1464.5,4656.1215625)(1480.5,4765.12675)(1496.5,4880.6024375)(1512.5,5003.2408125)(1528.5,5136.673125)(1544.5,5283.0321875)(1560.5,5444.2958125)(1576.5,5642.1679375)(1592.5,5967.94825)(1602,6241.055)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt, dashed, dash pattern=on 2pt off 8pt] coordinates {(1,0.004)(8.5,0.0501875)(24.5,0.1841875)(40.5,0.385375)(56.5,0.63275)(72.5,0.9063125)(88.5,1.2073125)(104.5,1.53075)(120.5,1.878625)(136.5,2.248)(152.5,2.6435)(168.5,3.0511875)(184.5,3.4775625)(200.5,3.919)(216.5,4.3756875)(232.5,4.8543125)(248.5,5.36475)(264.5,5.91125)(280.5,6.499375)(296.5,7.1506875)(312.5,7.8543125)(328.5,8.594375)(344.5,9.3725)(360.5,10.1935625)(376.5,11.092875)(392.5,12.035125)(408.5,13.0169375)(424.5,14.058375)(440.5,15.1575625)(456.5,16.3101875)(472.5,17.5235)(488.5,18.79075)(504.5,20.1346875)(520.5,21.5568125)(536.5,23.0485)(552.5,24.6221875)(568.5,26.2756875)(584.5,28.0125625)(600.5,29.863375)(616.5,31.8353125)(632.5,33.9231875)(648.5,36.124625)(664.5,38.4406875)(680.5,40.8851875)(696.5,43.4551875)(712.5,46.18625)(728.5,49.20325)(744.5,52.4388125)(760.5,55.897625)(776.5,59.6255)(792.5,63.556125)(808.5,67.7344375)(824.5,72.17275)(840.5,76.87375)(856.5,81.881625)(872.5,87.2705625)(888.5,92.9146875)(904.5,98.791)(920.5,104.930125)(936.5,111.3364375)(952.5,118.0683125)(968.5,125.098375)(984.5,132.4871875)(1000.5,140.3285625)(1016.5,148.5753125)(1032.5,157.201)(1048.5,166.2395)(1064.5,175.6414375)(1080.5,185.51025)(1096.5,195.957375)(1112.5,207.0698125)(1128.5,218.7384375)(1144.5,231.084125)(1160.5,244.2318125)(1176.5,257.92525)(1192.5,272.16775)(1208.5,287.037)(1224.5,302.7649375)(1240.5,319.7085625)(1256.5,337.873375)(1272.5,357.1653125)(1288.5,377.8138125)(1304.5,399.751125)(1320.5,424.0613125)(1336.5,450.661375)(1352.5,478.92)(1368.5,509.38125)(1384.5,543.107)(1400.5,581.489375)(1416.5,625.1093125)(1432.5,675.3388125)(1448.5,738.061)(1464.5,823.3106875)(1480.5,947.367625)(1496.5,1193.47425)(1512.5,1639.0449375)(1525,2121.9135555555554)(1531,2376.002)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt, dashdotted] coordinates {(1,1.017)(8,10.258933333333333)(23,29.255599999999998)(38,50.394800000000004)(53,72.92853333333333)(68,96.32026666666667)(83,120.54106666666667)(98,145.43706666666668)(113,170.85453333333334)(128,196.90246666666667)(143,223.42426666666665)(158,250.6794)(173,278.59159999999997)(188,307.04659999999996)(203,336.0550666666667)(218,365.4665333333333)(233,395.2475333333333)(248,425.3532)(263,455.8623333333333)(278,486.82626666666664)(293,518.2761333333334)(308,550.2016666666666)(323,582.5965333333334)(338,615.5299333333334)(353,648.8835333333333)(368,682.6476)(383,716.8438000000001)(398,751.3936)(413,786.4327333333333)(428,821.8758)(443,857.6266666666667)(458,893.7378666666667)(473,930.2567333333333)(488,967.1976)(503,1004.5210666666667)(518,1042.2291333333333)(533,1080.4326)(548,1119.0616666666667)(563,1158.132)(578,1197.6022666666665)(593,1237.5477333333333)(608,1278.0738666666666)(623,1319.0354)(638,1360.3044666666665)(653,1401.9102)(668,1443.9781333333333)(683,1486.5155333333335)(698,1529.4671333333333)(713,1573.0057333333334)(728,1617.0829333333334)(743,1661.8119333333334)(758,1707.0376)(773,1752.8307333333335)(788,1799.0442666666665)(803,1845.8358666666668)(818,1893.2626)(833,1941.298)(848,1990.1431333333333)(863,2039.6957333333335)(878,2089.9846666666667)(893,2141.0992666666666)(908,2193.0147333333334)(923,2245.761466666667)(938,2299.109466666667)(953,2353.2702666666664)(968,2408.4814666666666)(983,2464.6888)(998,2521.7824)(1013,2579.9236666666666)(1028,2639.587466666667)(1043,2701.1523333333334)(1058,2764.0695333333333)(1073,2827.9558666666667)(1088,2893.3823333333335)(1103,2960.3417999999997)(1118,3029.4202666666665)(1133,3100.2347999999997)(1148,3173.076866666667)(1163,3248.1202000000003)(1178,3326.137866666667)(1193,3407.703)(1208,3491.8776666666663)(1223,3578.656933333333)(1238,3668.5506)(1253,3762.1326666666664)(1268,3859.274933333333)(1283,3961.9732666666664)(1298,4070.4924666666666)(1313,4186.787066666667)(1328,4310.513400000001)(1343,4445.3554)(1358,4594.592466666667)(1373,4759.808933333334)(1388,4944.383400000001)(1403,5149.614333333333)(1418,5387.352599999999)(1433,5664.111533333333)(1448,5990.5318)(1463,6394.039400000001)(1478,6895.506266666666)(1493,7542.774266666666)(1502,7966.798)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt, dashed, dash pattern=on 8pt off 2pt] coordinates {(1,0.014)(8,0.1492666666666667)(23,0.43839999999999996)(38,0.7554)(53,1.0912666666666666)(68,1.446)(83,1.8062)(98,2.176)(113,2.551)(128,2.929)(143,3.318)(158,3.7084)(173,4.109)(188,4.517)(203,4.936)(218,5.362066666666666)(233,5.7984)(248,6.246666666666667)(263,6.708)(278,7.1781999999999995)(293,7.658066666666667)(308,8.147)(323,8.6444)(338,9.153)(353,9.669066666666668)(368,10.1942)(383,10.729)(398,11.269666666666666)(413,11.821)(428,12.376666666666667)(443,12.943)(458,13.514)(473,14.0964)(488,14.692)(503,15.2944)(518,15.9082)(533,16.533)(548,17.166666666666668)(563,17.8124)(578,18.47)(593,19.130666666666666)(608,19.802)(623,20.48)(638,21.169)(653,21.8642)(668,22.576)(683,23.3012)(698,24.039)(713,24.7904)(728,25.5542)(743,26.329066666666666)(758,27.1184)(773,27.927)(788,28.7524)(803,29.591866666666665)(818,30.448)(833,31.318)(848,32.201)(863,33.09986666666667)(878,34.01673333333333)(893,34.955666666666666)(908,35.91266666666667)(923,36.887)(938,37.8816)(953,38.8984)(968,39.93533333333333)(983,41.0048)(998,42.1114)(1013,43.2494)(1028,44.419066666666666)(1043,45.62166666666666)(1058,46.864466666666665)(1073,48.1382)(1088,49.4416)(1103,50.77926666666667)(1118,52.1594)(1133,53.60013333333333)(1148,55.10326666666667)(1163,56.676)(1178,58.32373333333333)(1193,60.0458)(1208,61.842400000000005)(1223,63.705933333333334)(1238,65.68766666666667)(1253,67.79246666666666)(1268,70.0094)(1283,72.42713333333333)(1298,75.1118)(1313,78.03226666666666)(1328,81.21066666666667)(1343,84.72706666666667)(1358,88.56126666666667)(1373,93.02126666666666)(1388,98.26266666666668)(1403,104.86593333333333)(1418,113.51339999999999)(1433,124.53553333333333)(1448,142.9748)(1463,195.25526666666667)(1473.5,343.9191666666667)(1478,471.791)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt, dashed, dash pattern=on 1pt off 2pt] coordinates {(1,0.014)(8.5,0.1705625)(24.5,0.5270625)(40.5,0.9435)(56.5,1.411375)(72.5,1.9261875)(88.5,2.471375)(104.5,3.0486875)(120.5,3.6491875)(136.5,4.26925)(152.5,4.9183125)(168.5,5.59575)(184.5,6.2953125)(200.5,7.0183125)(216.5,7.7696875)(232.5,8.552625)(248.5,9.361625)(264.5,10.20875)(280.5,11.08875)(296.5,11.9946875)(312.5,12.9349375)(328.5,13.899875)(344.5,14.886625)(360.5,15.894625)(376.5,16.93)(392.5,18.009)(408.5,19.1270625)(424.5,20.2855625)(440.5,21.4935)(456.5,22.751125)(472.5,24.069375)(488.5,25.446875)(504.5,26.8915)(520.5,28.4119375)(536.5,30.015375)(552.5,31.7089375)(568.5,33.4641875)(584.5,35.2725)(600.5,37.1615)(616.5,39.151125)(632.5,41.2473125)(648.5,43.431625)(664.5,45.6884375)(680.5,48.03575)(696.5,50.4545)(712.5,52.9450625)(728.5,55.5413125)(744.5,58.2293125)(760.5,60.9836875)(776.5,63.813375)(792.5,66.7405)(808.5,69.76075)(824.5,72.8876875)(840.5,76.128)(856.5,79.4839375)(872.5,82.9761875)(888.5,86.62225)(904.5,90.3834375)(920.5,94.26825)(936.5,98.3461875)(952.5,102.5914375)(968.5,107.029625)(984.5,111.6445625)(1000.5,116.4698125)(1016.5,121.504625)(1032.5,126.7716875)(1048.5,132.2453125)(1064.5,137.9896875)(1080.5,144.0614375)(1096.5,150.38)(1112.5,156.9101875)(1128.5,163.803625)(1144.5,171.048375)(1160.5,178.675875)(1176.5,186.5573125)(1192.5,194.7738125)(1208.5,203.287375)(1224.5,212.0685)(1240.5,221.080125)(1256.5,230.4013125)(1272.5,240.2630625)(1288.5,250.769125)(1304.5,261.9256875)(1320.5,273.955125)(1336.5,286.6981875)(1352.5,300.027625)(1368.5,314.1886875)(1384.5,329.4320625)(1400.5,345.72025)(1416.5,363.0874375)(1432.5,381.555625)(1448.5,401.5385)(1464.5,423.8074375)(1480.5,448.4118125)(1496.5,476.286125)(1512.5,510.4356875)(1528.5,553.1431875)(1544.5,607.709625)(1560.5,678.581375)(1576.5,800.2424375)(1587,950.0282)(1591,1061.191)};
\addlegendentry{Z3seq}

\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt, dashed, dash pattern=on 2pt off 4pt] coordinates {(1,0.005)(8.5,0.0531875)(24.5,0.1518125)(40.5,0.2625)(56.5,0.3745)(72.5,0.4865)(88.5,0.5985)(104.5,0.7105)(120.5,0.8253125)(136.5,0.952)(152.5,1.08)(168.5,1.208)(184.5,1.336)(200.5,1.464375)(216.5,1.6035)(232.5,1.7475)(248.5,1.8915)(264.5,2.0355)(280.5,2.1795)(296.5,2.3235)(312.5,2.4675)(328.5,2.6116875)(344.5,2.766)(360.5,2.926)(376.5,3.086)(392.5,3.246)(408.5,3.406)(424.5,3.566)(440.5,3.726)(456.5,3.8873125)(472.5,4.0605)(488.5,4.2365)(504.5,4.4125)(520.5,4.5885)(536.5,4.7645)(552.5,4.9439375)(568.5,5.135)(584.5,5.327)(600.5,5.519)(616.5,5.7175625)(632.5,5.9255)(648.5,6.134125)(664.5,6.354)(680.5,6.5789375)(696.5,6.8155)(712.5,7.056125)(728.5,7.308)(744.5,7.568125)(760.5,7.840125)(776.5,8.124)(792.5,8.4185625)(808.5,8.7234375)(824.5,9.04)(840.5,9.3665625)(856.5,9.7038125)(872.5,10.053)(888.5,10.4084375)(904.5,10.7755)(920.5,11.147625)(936.5,11.5323125)(952.5,11.9296875)(968.5,12.340625)(984.5,12.7685)(1000.5,13.2081875)(1016.5,13.66875)(1032.5,14.14875)(1048.5,14.64475)(1064.5,15.15725)(1080.5,15.691375)(1096.5,16.2514375)(1112.5,16.8374375)(1128.5,17.4513125)(1144.5,18.10075)(1160.5,18.782875)(1176.5,19.5125)(1192.5,20.281875)(1208.5,21.093125)(1224.5,21.9540625)(1240.5,22.867)(1256.5,23.8339375)(1272.5,24.876125)(1288.5,26.007125)(1304.5,27.2279375)(1320.5,28.564875)(1336.5,29.9903125)(1352.5,31.529875)(1368.5,33.237)(1384.5,35.1899375)(1400.5,37.4680625)(1416.5,40.07125)(1432.5,43.1341875)(1448.5,46.8099375)(1464.5,51.341)(1480.5,57.03675)(1496.5,64.4295)(1512.5,73.6899375)(1528.5,86.0960625)(1544.5,108.3425)(1560.5,174.1435625)(1569.5,260.0555)(1572,300.23)};
\addlegendentry{Z3str3RE}
